The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-20 dit-paper_ieee.tex
Reworded

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:
		\begin{theorem}
			\begin{equation*}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*}
		\end{theorem}
        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time. Therefore the system is unfeasible.

>>>>

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:
		\begin{theorem}
			\begin{equation*}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*}
		\end{theorem}
        It is easy to see that the condition is at least necessary, as if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time. Therefore the system would be unfeasible.
